---
Function: TARIFF IMPACTS ON PORTFOLIO MANAGEMENT
Author: Hang BUI
Student ID: 22070661
Class: FDA 2025 Spring
Version and Date: 1.0 20250524 Initial codes
---
#1. List of 50 top performing stocks in the U.S
```{r}
# Load required libraries
library(quantmod)
library(dplyr)
library(readr)
library(lubridate)

# List of 50 top-performing S&P 500 stocks (by market cap and performance)
top_50_stocks <- c(
  "AAPL", "MSFT", "GOOGL", "AMZN", "NVDA", "TSLA", "META", "BRK-B", "UNH", "JNJ",
  "V", "WMT", "JPM", "PG", "MA", "HD", "CVX", "ABBV", "BAC", "PFE",
  "KO", "AVGO", "PEP", "TMO", "COST", "DIS", "ABT", "ACN", "NFLX", "ADBE",
  "CRM", "VZ", "DHR", "XOM", "NKE", "MRK", "T", "CSCO", "INTC", "WFC",
  "AMD", "TXN", "LLY", "QCOM", "NEE", "UPS", "PM", "LOW", "HON", "IBM"
)

# Set date range  
start_date <- "2024-01-01"  
end_date <- Sys.Date()

# Function to download stock data safely
download_stock_data <- function(symbol, start, end) {
  tryCatch({
    cat("Downloading data for:", symbol, "\n")
    data <- getSymbols(symbol, 
                      src = "yahoo", 
                      from = start, 
                      to = end, 
                      auto.assign = FALSE)
    
    # Convert to data frame and add symbol column
    df <- data.frame(
      Date = index(data),
      Symbol = symbol,
      Open = as.numeric(Op(data)),
      High = as.numeric(Hi(data)),
      Low = as.numeric(Lo(data)),
      Close = as.numeric(Cl(data)),
      Volume = as.numeric(Vo(data)),
      Adjusted = as.numeric(Ad(data))
    )
    
    return(df)
  }, error = function(e) {
    cat("Error downloading", symbol, ":", e$message, "\n")
    return(NULL)
  })
}

# Download data for all stocks
cat("Starting download of stock data...\n")
cat("Date range:", as.character(start_date), "to", as.character(end_date), "\n\n")

all_stock_data <- list()

for (stock in top_50_stocks) {
  stock_data <- download_stock_data(stock, start_date, end_date)
  if (!is.null(stock_data)) {
    all_stock_data[[stock]] <- stock_data
  }
  Sys.sleep(0.5)  # Be respectful to Yahoo Finance API
}

# Combine all data into one data frame
combined_data <- bind_rows(all_stock_data)

write_csv(combined_data, "D:/BUI THU HANG/NĂM BA/FDA/FDA 2025 Spring Hang BUI Top50 Stock.csv")
cat("Data saved as CSV: FDA 2025 Spring Hang BUI Top50 Stock\n")
```
#2. The impact of US presidential election  
##2.1 The impact of US presidential election on 50 corporations
```{r}
library(dplyr)
library(ggplot2)
library(readr)
library(lubridate)
library(scales)

# Đọc dữ liệu
stock_data <- read_csv("D:/BUI THU HANG/NĂM BA/FDA/FDA 2025 Spring Hang BUI Top50 Stock.csv")

# Thông tin ngành
stock_categories <- data.frame(
  Symbol = c("AAPL", "MSFT", "GOOGL", "AMZN", "NVDA", "TSLA", "META", "BRK-B", "UNH", "JNJ",
             "V", "WMT", "JPM", "PG", "MA", "HD", "CVX", "ABBV", "BAC", "PFE",
             "KO", "AVGO", "PEP", "TMO", "COST", "DIS", "ABT", "ACN", "NFLX", "ADBE",
             "CRM", "VZ", "DHR", "XOM", "NKE", "MRK", "T", "CSCO", "INTC", "WFC",
             "AMD", "TXN", "LLY", "QCOM", "NEE", "UPS", "PM", "LOW", "HON", "IBM"),
  Sector = c("Technology", "Technology", "Technology", "Consumer Discretionary", "Technology", 
             "Consumer Discretionary", "Technology", "Financial", "Healthcare", "Healthcare",
             "Financial", "Consumer Staples", "Financial", "Consumer Staples", "Financial", 
             "Consumer Discretionary", "Energy", "Healthcare", "Financial", "Healthcare",
             "Consumer Staples", "Technology", "Consumer Staples", "Healthcare", "Consumer Staples", 
             "Communication", "Healthcare", "Technology", "Communication", "Technology",
             "Technology", "Communication", "Healthcare", "Energy", "Consumer Discretionary", 
             "Healthcare", "Communication", "Technology", "Technology", "Financial",
             "Technology", "Technology", "Healthcare", "Technology", "Utilities", 
             "Industrials", "Consumer Staples", "Consumer Discretionary", "Industrials", "Technology")
)

stock_data <- stock_data %>% left_join(stock_categories, by = "Symbol")

# Các mốc sự kiện : chỉ lấy events trong khoảng thời gian cần plot
tariff_dates <- data.frame(
  Date = as.Date(c("2024-11-05", "2025-04-02", "2025-04-17")),
  Event = c("US Election", "Tariff Announce", "Tariff Defer")
)

plot_data <- stock_data %>%
  mutate(Date = as.Date(Date))

events_in_range <- tariff_dates %>%
  filter(!Event %in% c("Tariff Announce", "Tariff Defer"))

# Tính max y value trước khi vẽ
max_price <- max(plot_data$Adjusted, na.rm = TRUE)

# Vẽ biểu đồ với tất cả 50 công ty  
p1 <- ggplot(plot_data, aes(x = Date, y = Adjusted, color = Symbol)) +
  geom_line(linewidth = 0.5, alpha = 0.7) +
  scale_y_continuous(labels = dollar_format(prefix = "$")) +
  scale_x_date(
    limits = as.Date(c("2024-10-01", "2025-05-31")),
    date_breaks = "1 month",
    date_labels = "%b %Y"
  ) +
  labs(
    title = "Stock Prices of Top 50 US Corporations",
    subtitle = "after US Election",
    x = "Date", y = "Adjusted Close Price (USD)",
    color = "Company"
  ) +
  geom_vline(data = events_in_range, aes(xintercept = Date), 
             linetype = "dashed", color = "red", linewidth = 1) +
  geom_text(data = events_in_range, aes(x = Date, y = max_price * 0.95,
                                        label = Event), 
            angle = 90, vjust = -0.5, hjust = 1, color = "red", size = 3) +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

print(p1)

# Tạo thêm biểu đồ theo sector để dễ nhìn hơn
sector_data <- plot_data %>%
  group_by(Date, Sector) %>%
  summarise(Avg_Price = mean(Adjusted, na.rm = TRUE), .groups = 'drop')

p2 <- ggplot(sector_data, aes(x = Date, y = Avg_Price, color = Sector)) +
  geom_line(linewidth = 1.2) +
  scale_y_continuous(labels = dollar_format(prefix = "$")) +
  labs(
    title = "Average Stock Prices by Sector",
    subtitle = "Top 50 S&P Companies - Election",
    x = "Date", y = "Average Adjusted Close Price (USD)",
    color = "Sector"
  ) +
  geom_vline(data = events_in_range, aes(xintercept = Date), 
             linetype = "dashed", color = "black", linewidth = 1) +
  geom_text(data = events_in_range, aes(x = Date, y = max(sector_data$Avg_Price) * 0.95,
                                    label = Event), 
            angle = 90, vjust = -0.5, hjust = 1, color = "black", size = 3) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

print(p2)

```

##2.2 The impact of US presidential election on Google (GOOGL)
```{r}
stock_data <- stock_data %>% left_join(stock_categories, by = "Symbol")

# Các mốc sự kiện - SỬA LỖI: chỉ lấy events trong khoảng thời gian cần plot
tariff_dates <- data.frame(
  Date = as.Date(c("2024-11-05", "2025-04-02", "2025-04-17")),
  Event = c("US Election", "Tariff Announce", "Tariff Defer")
)

plot_data <- stock_data %>%
  mutate(Date = as.Date(Date))

events_in_range <- tariff_dates %>%
  filter(!Event %in% c("Tariff Announce", "Tariff Defer"))

# SỬA LỖI: Tính max y value trước khi vẽ
max_price <- max(plot_data$Adjusted, na.rm = TRUE)

# Lọc dữ liệu cho GOOGL
tsla_data <- plot_data %>% filter(Symbol == "GOOGL")

# Vẽ biểu đồ cho GOOGL
p_tsla <- ggplot(tsla_data, aes(x = Date, y = Adjusted)) +
  geom_line(color = "blue", linewidth = 1) +
  scale_y_continuous(labels = dollar_format(prefix = "$")) +
  scale_x_date(
    limits = as.Date(c("2024-10-01", "2025-05-31")),
    date_breaks = "1 month",
    date_labels = "%b %Y"
  ) +
  labs(
    title = "Stock Price of Google (GOOGL)",
    subtitle = "after US Election",
    x = "Date", y = "Adjusted Close Price (USD)"
  ) +
  geom_vline(data = events_in_range, aes(xintercept = Date), 
             linetype = "dashed", color = "red", linewidth = 1) +
  geom_text(data = events_in_range, aes(x = Date, y = max(tsla_data$Adjusted, na.rm = TRUE) * 0.95,
                                        label = Event), 
            angle = 90, vjust = -0.5, hjust = 1, color = "red", size = 3) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

print(p_tsla)

```

#3. The impact of recent tariff policy developments 
##3.1 The impact of recent tariff policy developments on 50 corporations

```{r}
library(dplyr)
library(ggplot2)
library(readr)
library(lubridate)
library(scales)

# Đọc dữ liệu
stock_data <- read_csv("D:/BUI THU HANG/NĂM BA/FDA/FDA 2025 Spring Hang BUI Top50 Stock.csv")

# Thông tin ngành
stock_categories <- data.frame(
  Symbol = c("AAPL", "MSFT", "GOOGL", "AMZN", "NVDA", "TSLA", "META", "BRK-B", "UNH", "JNJ",
             "V", "WMT", "JPM", "PG", "MA", "HD", "CVX", "ABBV", "BAC", "PFE",
             "KO", "AVGO", "PEP", "TMO", "COST", "DIS", "ABT", "ACN", "NFLX", "ADBE",
             "CRM", "VZ", "DHR", "XOM", "NKE", "MRK", "T", "CSCO", "INTC", "WFC",
             "AMD", "TXN", "LLY", "QCOM", "NEE", "UPS", "PM", "LOW", "HON", "IBM"),
  Sector = c("Technology", "Technology", "Technology", "Consumer Discretionary", "Technology", 
             "Consumer Discretionary", "Technology", "Financial", "Healthcare", "Healthcare",
             "Financial", "Consumer Staples", "Financial", "Consumer Staples", "Financial", 
             "Consumer Discretionary", "Energy", "Healthcare", "Financial", "Healthcare",
             "Consumer Staples", "Technology", "Consumer Staples", "Healthcare", "Consumer Staples", 
             "Communication", "Healthcare", "Technology", "Communication", "Technology",
             "Technology", "Communication", "Healthcare", "Energy", "Consumer Discretionary", 
             "Healthcare", "Communication", "Technology", "Technology", "Financial",
             "Technology", "Technology", "Healthcare", "Technology", "Utilities", 
             "Industrials", "Consumer Staples", "Consumer Discretionary", "Industrials", "Technology")
)

stock_data <- stock_data %>% left_join(stock_categories, by = "Symbol")

# Các mốc sự kiện - SỬA LỖI: chỉ lấy events trong khoảng thời gian cần plot
tariff_dates <- data.frame(
  Date = as.Date(c("2024-11-05", "2025-04-02", "2025-04-17")),
  Event = c("US Election", "Tariff Announce", "Tariff Defer")
)

plot_data <- stock_data %>%
  mutate(Date = as.Date(Date))

events_in_range <- tariff_dates %>%
  filter(Event %in% c("Tariff Announce", "Tariff Defer"))

# SỬA LỖI: Tính max y value trước khi vẽ
max_price <- max(plot_data$Adjusted, na.rm = TRUE)

# Vẽ biểu đồ với tất cả 50 công ty - SỬA LỖI size thành linewidth
p1 <- ggplot(plot_data, aes(x = Date, y = Adjusted, color = Symbol)) +
  geom_line(linewidth = 0.5, alpha = 0.7) +
  scale_y_continuous(labels = dollar_format(prefix = "$")) +
  scale_x_date(
    limits = as.Date(c("2024-10-01", "2025-05-31")),
    date_breaks = "1 month",
    date_labels = "%b %Y"
  ) +
  labs(
    title = "Stock Prices of Top 50 US Corporations",
    subtitle = "after Tariff Policy Dates",
    x = "Date", y = "Adjusted Close Price (USD)",
    color = "Company"
  ) +
  geom_vline(data = events_in_range, aes(xintercept = Date), 
             linetype = "dashed", color = "red", linewidth = 1) +
  geom_text(data = events_in_range, aes(x = Date, y = max_price * 0.95,
                                        label = Event), 
            angle = 90, vjust = -0.5, hjust = 1, color = "red", size = 3) +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

print(p1)

# Tạo thêm biểu đồ theo sector để dễ nhìn hơn
sector_data <- plot_data %>%
  group_by(Date, Sector) %>%
  summarise(Avg_Price = mean(Adjusted, na.rm = TRUE), .groups = 'drop')

p2 <- ggplot(sector_data, aes(x = Date, y = Avg_Price, color = Sector)) +
  geom_line(linewidth = 1.2) +
  scale_y_continuous(labels = dollar_format(prefix = "$")) +
  labs(
    title = "Average Stock Prices by Sector",
    subtitle = "Top 50 S&P Companies - Tariff Impact",
    x = "Date", y = "Average Adjusted Close Price (USD)",
    color = "Sector"
  ) +
  geom_vline(data = events_in_range, aes(xintercept = Date), 
             linetype = "dashed", color = "black", linewidth = 1) +
  geom_text(data = events_in_range, aes(x = Date, y = max(sector_data$Avg_Price) * 0.95,
                                    label = Event), 
            angle = 90, vjust = -0.5, hjust = 1, color = "black", size = 3) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

print(p2)
```

##3.2 The impact of recent tariff policy developments on Google (GOOGL)
```{r}
stock_data <- stock_data %>% left_join(stock_categories, by = "Symbol")

# Các mốc sự kiện - SỬA LỖI: chỉ lấy events trong khoảng thời gian cần plot
tariff_dates <- data.frame(
  Date = as.Date(c("2024-11-05", "2025-04-02", "2025-04-17")),
  Event = c("US Election", "Tariff Announce", "Tariff Defer")
)

plot_data <- stock_data %>%
  mutate(Date = as.Date(Date))

events_in_range <- tariff_dates %>%
  filter(Event %in% c("Tariff Announce", "Tariff Defer"))

# SỬA LỖI: Tính max y value trước khi vẽ
max_price <- max(plot_data$Adjusted, na.rm = TRUE)

# Lọc dữ liệu cho GOOGL
tsla_data <- plot_data %>% filter(Symbol == "TSLA")

# Vẽ biểu đồ cho GOOGL
p_tsla <- ggplot(tsla_data, aes(x = Date, y = Adjusted)) +
  geom_line(color = "blue", linewidth = 1) +
  scale_y_continuous(labels = dollar_format(prefix = "$")) +
  scale_x_date(
    limits = as.Date(c("2024-10-01", "2025-05-31")),
    date_breaks = "1 month",
    date_labels = "%b %Y"
  ) +
  labs(
    title = "Stock Price of Google (GOOGL)",
    subtitle = "after Tariff Policy Dates",
    x = "Date", y = "Adjusted Close Price (USD)"
  ) +
  geom_vline(data = events_in_range, aes(xintercept = Date), 
             linetype = "dashed", color = "red", linewidth = 1) +
  geom_text(data = events_in_range, aes(x = Date, y = max(tsla_data$Adjusted, na.rm = TRUE) * 0.95,
                                        label = Event), 
            angle = 90, vjust = -0.5, hjust = 1, color = "red", size = 3) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

print(p_tsla)

```
